---
title: "Ramen Rating By Types"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(dplyr)
library(ggridges)
library(plotly)
library(patchwork)
library(gplots)
```

```{r clean, include=FALSE}
tidy_ramen = 
  read_csv("./ramen-ratings.csv") %>% 
  janitor::clean_names() %>% 
  drop_na(style)%>% 
  separate(top_ten, into = c("year", "rank"), sep = " #", convert = TRUE) %>% 
  mutate(
    style = factor(style),
    country = factor(country),
    brand = factor(brand),
    stars = as.numeric(stars)
  )
```

## Background Introduction 
In this Ramen dataset, there are `r nrow(count(tidy_ramen, style))` types of ramen packaging. We wonder if different pakcaging may affect the texture and flavor of ramen. In the following adventure, let's see if the packaging makes a difference!

## Distribution of Rating by style
```{r}
distri_various = 
  tidy_ramen %>%
  drop_na(stars) %>%
  ggplot(aes(x = style, y = stars, color = style)) + 
  geom_boxplot() +
  labs(
    title = "Rating Distribution",
    x = "Ramen Style",
    y = "Rating Stars"
  )
distri_various
```
## Analysis of Distribution

We see that from the boxplot above, Can and Bar packaging of ramen only have one ramen each. Therefore, we drop these two styles because they are not representative.

```{r}
new_ramen = 
  select(tidy_ramen, style, stars) %>%
  filter(style %in% c("Bowl", "Box", "Cup", "Pack", "Tray"))

test <- chisq.test(new_ramen$style, new_ramen$stars)
test
```
The Chi-squared test yields a p-value that is greater than 0.05 so we failed to reject null hypothesis and conclude that styles of ramen does not affect the rating.




